---
title: "Handaxes from Furze Platt (Berkshire, United-Kingdom). A quantative study of Lower Palaeolithic Axes in South East England"
author: ""
date: ""
bibliography: references.bib
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
pagetitle: "1. Report with Rmarkdown - Practice"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## Not run
# install.packages("archdata")
library(archdata)
```

Study of the handaxes from the Furze Platt site stored at the Royal Ontario Museum.

> in the YAML header
>   - update the **author** name, and the **date**
>   - add a new line for an **abstract**
>   - emphise the first part of the **title** with HTML tags (letter size)
>   - update the `references.bib` with 

```{r handaxes}
data("Handaxes")
```

Sometimes it is useful to show exactly how the computation has been done (echo = True)

```{r pressure, echo=True}
plot(pressure)
```

# Authoring framework (10 min)

Authoring framework for data science, or data-driven document, combining code and narrative text. 




Rmarkdown combines

* parts in R code

* parts in markdown syntax. 

# Theory (30 min)

## Writing

### Markdown syntax

Markdown syntax is plain text used in GitHub, Sketchfab, Slack, bookdown, etc. Editing in RStudio, support objects BibTex, 3D, videos, etc. Export in HTML, PDF, LaTex, etc. For example:

* this Rmarkdown document/webpage
* a R handbook in bookdown: @Hinz21
* ...

### Rmarkdown structure


Rmarkdown structure (bandeau)

#### Code chunks

* header
  - include
  - echo
  - eval
  - caption
  - etc.
* body
  - R code

#### Narrative text

Markdown syntax

* **bold**, *italic*, `code`, <span style="color:red">color</span>
* [hyperlinks](https://rmarkdown.rstudio.com/), [bookmarks](#practice)
* lists
  1.
  2.
  3.
* dataframe
* footnotes^[I am a footnote]
* calls
  - variable: 'my.sum = `r my.sum`'
  - chunk or figure
* etc.

##### YAML header

author, date, table of contents, bibliographic references

## Publishing

PDF, HTML, etc.

# Practice (120 min) {#practice}



# References


















