---
title: "<span style='font-size: 40px'><b>R4Archaeologists</b></style> <span style='font-size: 30px'> <br>Report data analysis with Rmarkdown <br></style>"
# abstract: "" 
author: "Thomas Huet"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: references.bib
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
pagetitle: "Report with Rmarkdown"
---

```{r, echo=FALSE}
url.root <- "https://raw.githubusercontent.com/zoometh/oxford/main/R4Archaeologists/www/"
htmltools::img(src = paste0(url.root, "logo.png"), 
               alt = 'logo', 
               width = '150px',
               style = 'position:absolute; top:0; right:0; padding:10px;')
```

# Rmarkdown introduction (45 min)

Authoring framework for data science, or data-driven document, combining:

* parts in R code

* parts in markdown syntax. 

```{r my.chunk, echo=FALSE, out.width="50%", fig.cap="Pisa"}
my.sum <- 1 + 1
my.img <- paste0(url.root, "pisa.png")
knitr::include_graphics(my.img)
```

Markdown syntax is plain text used in GitHub, Sketchfab, Slack, bookdown, etc. Editing in RStudio, support objects BibTex, 3D, videos, etc. Export in HTML, PDF, LaTex, etc. For example:

* this Rmarkdown document/webpage
* a R handbook in bookdown: @Hinz21
* ...

## Environment

packages rstudio, knitr, etc.

## Rmarkdown structure

### Code chunks

#### header

include, echo, eval, caption, etc.

#### body

R code

### Narrative text

Markdown syntax  

##### Syntax overview

[Basic syntax](https://www.markdownguide.org/basic-syntax/)

* **bold**, *italic*, `code`, <span style="color:red">color</span>
* [hyperlinks](https://rmarkdown.rstudio.com/), [bookmarks](#practice)
* lists
  - 1
  - 2
  - 3
* dataframe
* footnotes^[I am a footnote]
* call of variable: `r my.sum`, call of chunk
* etc.

#### YAML header

author, date, table of contents, bibliographic references

## Practice (115 min) {#practice}

* Include R code in a code chunk
* Use of markdown syntax
* add bibliographical references




















